Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-10 prop_letter.tex
prop_letter.tex \section{Born} Updating...

Since $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, every function~$\iota_{1}\circ\mu$
on a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
Hilbert space, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
is not a QIVPM. This highlights the necessity of the conditions to
guarantee $\iota\circ\mu$ is always a QIVPM.

\begin{thm}\label{thm:iota-statements}The following two statements
are equivalent:
\begin{enumerate}
\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is subject to Eqs.~(\ref{eq:iota-constraints}) and satisfies that
for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
\begin{equation}
\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
\end{aligned}
\label{eq:iota-Inclusion}
\end{equation}
\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
on any Hilbert space~$\Hilb$.
\end{enumerate}
\end{thm}

>>>>

Since $\iota_{1}$ defined in Eq.~(\ref{eq:iota}) satisfies Eqs.~(\ref{eq:iota-constraints})
and Eq.~(\ref{eq:iota-add})~\citep{HOSTunpublished}, every function~$\iota_{1}\circ\mu$
on a three-dimensional Hilbert space is a QIVPM. However, on four-dimensional
Hilbert space, $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$
is not a QIVPM. This highlights the necessity to have conditions disregarding
the dimension of the Hilbert space.

\begin{thm}\label{thm:iota-statements}The following two statements
are equivalent:
\begin{enumerate}
\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
satisfies Eqs.~(\ref{eq:iota-constraints}) and for any three numbers~$x_{0}$,
$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies
\begin{equation}
\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
\end{aligned}
\label{eq:iota-Inclusion}
\end{equation}
\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
on any Hilbert space~$\Hilb$.
\end{enumerate}
\end{thm}
